\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-11 k-planar.tex
minor edits

  An important aspect of our result for $1$-planar graphs is that graph $H$ in the product is planar and has treewidth $3$, i.e., it has simple treewidth $3$.  In a more recent application of product structure \citet{BDJM} show that such graphs have $\ell$-vertex rankings using $O(\log n/\log\log\log n)$ colours, and this is tight. This result requires that $H$ have simple treewidth $3$, even treewidth $3$ is not sufficient.

  Finally, while cleaning up this proof we have also improved the constant from $30$ to $7$. The proof is quite similar to the previous proof except that graph $G'$ is obtained by removing both crossing edges involved in a crossing (the spars of a kite), rather than just one.  We thank the referee for forcing us to write this proof more carefully so that we could discover this improvement. 
}

@@

@@

>>>>

  An important aspect of our result for $1$-planar graphs is that graph $H$ in the product is planar and has treewidth $3$, i.e., it has simple treewidth $3$.  In a more recent application of product structure \citet{BDJM} show that such graphs have $\ell$-vertex rankings using $O(\log n/\log\log\log n)$ colours, and this is tight. This result requires that $H$ have simple treewidth $3$, even treewidth $3$ is not sufficient.
}

\note{DW}{I will rewrite the intro to this subsection once we decide what our results are.}

@@

\begin{cor}
	\label{New1Planar}
	Every 1-planar graph is contained in $H \boxtimes P \boxtimes K_8$ for some graph $H$ with $\tw(H) \leq 3$ and for some path $P$.
\end{cor}

@@

\begin{cor}
	\label{NewMapGraph}
	Every $d$-map graph is contained in $H \boxtimes P \boxtimes K_{ d  \floor{d/2} }$ for some graph $H$ with $\tw(H) \leq 3$ and for some path $P$.
\end{cor}
